### 2022-05-18 manuscript.Rmd
Use journal abbreviations

To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@gee2005; @efron1993]. To this end, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration. We then checked if the meta-analytic effect size and heterogeneity remained constant or if it was sensitive against the influence of any individual experiment (Supplementary Table\ \@ref(tab:tabs3)).

>>>>

To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@efron1993]. To this end, we refitted the Bayesian three-level model repeatedly while leaving out one of the original experiments on every iteration. We then checked if the meta-analytic effect size and heterogeneity remained constant or if it was sensitive against the influence of any individual experiment (Supplementary Table\ \@ref(tab:tabs3)).
